### 2021-07-01 paper_v2/coverletter/netsMatter_coverLetter.tex
paper revisions per chat

This letter accompanies our submission of a manuscript for your consideration. The manuscript ``Taking Dyads Seriously'' introduces the Additive and Multiplicative Effects (AME) framework for conducting inference in the context of the dependencies that we often observe in dyadic data. In submitting this paper, we feel as though it is necessary to first provide some background information. \\[1ex]

Among some political scientists using statistical models to analyze network data there has emerged a dispute between the advocates of the Exponential Random Graph (ERGM) model and those building on the ``latent space'' approach pioneered by Hoff, Raftery, and Handcock. This unproductive fight is not mirrored in the statistical or broader networks literature, as in those communities people recognize these models as having quite distinct goals. These models having differing goals is something that I also believe and which is why in a recent ERGM related article I reviewed for PSRM, I did not express any need for the authors to engage in this dispute. \\[1ex]

>>>>

This letter accompanies our submission of a manuscript for your consideration. The manuscript ``Taking Dyads Seriously'' discusses and tests the utility of the Additive and Multiplicative Effects (AME) framework for conducting inference in the context of the dependencies that often occur in dyadic data. In submitting this paper, we feel as though it is necessary to first provide some background information. \\[1ex]

Among some political scientists using statistical models to analyze network data there has emerged a dispute between the advocates of the Exponential Random Graph (ERGM) model and those building on the ``latent space'' approach pioneered by Hoff, Raftery, and Handcock. This unproductive fight is not mirrored in the statistical or broader networks literature, as in those communities people recognize these models as having quite distinct goals. These models having differing goals is something that I also believe and which is why in a recent ERGM related article I reviewed for PSRM, I did not express any need for the authors to engage in a lengthy contrast of their approach with latent variable models. \\[1ex]
